flowers-pilot-analysis

### 2021-07-27 code/aa-flowers-pilot_analysis.Rmd
add prelim figs

```{r set-up, include=F}
library(tidyverse)
library(jsonlite)
library(here)
source(here("code/preprocessing/00_preprocessing_functions.R"))
theme_set(theme_classic())

##Data import constants
date_start=lubridate::ymd('2021-07-19')
fig_path=here("figs")

# Pre-process
Remove joined_data and uncomment the following block to rerun the preprocessing scripts
```{r process-data, message=FALSE, warning=FALSE}
data_list <- c("technical_pilots", "collabmulti_pilot0",
               "collabmulti_20", "compet_20")
process_all_data(data_list)
join_all_data()
```

@@

```{r}
#exclude BLOCKS with <12 completed (all 3 participants responded) rounds
#exclude trial runs

rounds_exclude <- d.rounds %>% group_by(gameId, blockNum) %>% tally() %>% filter(n!=36) %>% select(gameId,blockNum)

d.rounds.final <-  d.rounds %>% anti_join(rounds_exclude)
d.raw_chat.final <- d.raw_chat %>% anti_join(rounds_exclude) %>% write_csv(here("data/processed_data/joined_data/filtered_raw_chat.csv"))
```

@@

d.by_game_metrics <- d.rounds.final%>% 
  left_join(d.games %>% select(-createdAt)) %>%  
  left_join(d.round_word_counts) %>%
  left_join(game_completion %>% select(gameId, num_rounds)) %>%
  mutate(languageCondition = ifelse(chatEnabled, "Lang", "Nonlang"),
         fullCondition = paste(condition, languageCondition, sep = "-")) %>% 
  #group by game
  group_by(gameId, name,condition, languageCondition, fullCondition, gameLength,num_rounds) %>%
  summarize(groupPoints = sum(playerUtility, na.rm = T),
            groupNumWords = sum(total_num_words, na.rm = T),
            groupNumChars = sum(total_num_chars, na.rm = T))%>%
  mutate(groupPoints = ifelse(condition=="coopCartel", 
                               groupPoints/3, groupPoints)) %>% 
  #adjust for max
  mutate(adjustedPoints = case_when(condition == "coopCartel" ~ groupPoints/ ((12*3)*48),
                                    condition == "coopMulti" ~ groupPoints/ ((12+11+10)*48),
                                    condition == "competCartel" ~ groupPoints/ ((12+11+10)*48)))
```

@@

```{r, fig.height=3, fig.width=5}
d.by_game_metrics%>% 
  ggplot(aes(x = languageCondition, y = groupPoints, color = condition, shape = languageCondition)) + 
  geom_jitter(width = .2, alpha = .5) +
  stat_summary(fun.data = "mean_cl_boot")+
  facet_grid(cols = vars(condition)) + labs(x = "Language Condition", y = "Points Earned by Group", title = "Points Earned by Group") + theme_classic() + theme(legend.position = "none")

ggsave(here(fig_path, "points_distirbution_raw.png"))
```

@@

```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>%
  ggplot(aes(x = languageCondition, y = adjustedPoints, color = condition, shape = languageCondition)) + 
  geom_jitter(width = .2, alpha = .5) +
  stat_summary(fun.data = "mean_cl_boot")+
  facet_grid(cols = vars(condition)) + labs(x = "Language Condition", y = "Points Earned by Group (Max Adjusted)", title = "Adjusted Points by Group") + theme_classic() + theme(legend.position = "none")

ggsave(here(fig_path, "points_distirbution_adjusted.png"))
```

### Time
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>%
  ggplot(aes(x = languageCondition, y = gameLength/60, color = condition, shape = languageCondition)) + 
  geom_jitter(width = .2, alpha = .5) +
  stat_summary(fun.data = "mean_cl_boot")+
  facet_grid(cols = vars(condition))+ labs(y = "Time (In Minutes)", title = "Game Length")+theme_classic() + theme(legend.position = "none")
```
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>%
  ggplot(aes(x = languageCondition, y = log(gameLength/60), color = condition, shape = languageCondition)) + 
  geom_jitter(width = .2, alpha = .5) +
  stat_summary(fun.data = "mean_cl_boot")+
  facet_grid(cols = vars(condition))+ labs(y = "Time (In Log Minutes)", title = "Game Length (Log Mins)")+theme_classic() + theme(legend.position = "none")
```

### Number of Words
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>%
  ggplot(aes(x = languageCondition, y = groupNumWords, color = condition, shape = languageCondition)) + 
  geom_jitter(width = .2, alpha = .5) +
  stat_summary(fun.data = "mean_cl_boot")+
  facet_grid(cols = vars(condition))+ labs(y = "N. Words", title = "Number of Words Exchanged")+theme_classic() + theme(legend.position = "none")
```
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>%
  ggplot(aes(x = languageCondition, y = log(groupNumWords), color = condition, shape = languageCondition)) + 
  geom_jitter(width = .2, alpha = .5) +
  stat_summary(fun.data = "mean_cl_boot")+
  facet_grid(cols = vars(condition))+ labs(y = "Log N. Words Exchanged")+theme_classic() + theme(legend.position = "none")
```

#### Condition Effects on Language Use
```{r}
d.round_word_counts %>%left_join(d.games %>% 
                                   select(gameId, condition,chatEnabled)) %>% 
  mutate(languageCondition = ifelse(chatEnabled, "Lang", "Nonlang"),
         fullCondition = paste(condition, languageCondition, sep = "-"),
         block_name = paste0("Block ", blockNum)) %>%
    filter(languageCondition == "Lang") %>%
  group_by(gameId, fullCondition, languageCondition, condition) %>% 
  summarize(groupNumWords = sum(total_num_words, na.rm = T)) %>% 
  ggplot() + geom_density(aes(x = groupNumWords, fill = condition), alpha = .5, adjust = .7)
```

## Scatters
### Time x Points
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>%
  ggplot(aes(x = gameLength/60, y = groupPoints, color = condition)) + 
  geom_point(alpha = .5) +
  geom_smooth(method=lm)+
  facet_grid(cols = vars(condition))+ labs(x = "Game length (in Minutes)", y = "Points Earned by Group")+theme_classic() + theme(legend.position = "none")
```

```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>%
  ggplot(aes(x = gameLength/60, y = groupPoints, color = log(groupNumWords))) + 
  geom_point(alpha = .5) +
  geom_smooth(method=lm)+
  facet_grid(cols = vars(condition))+ labs(x = "Game length (in Minutes)", y = "Points Earned by Group")+theme_classic() + scale_color_steps()
```

```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>%
  ggplot(aes(x = gameLength/60, y = groupPoints, color = condition)) + 
  geom_point(alpha = .5) +
  geom_smooth(method=lm)+
  labs(x = "Game length (in Minutes)", y = "Points Earned by Group")+theme_classic()
```

Log
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>% 
  ggplot(aes(x = log(gameLength/60), y = groupPoints, color = condition)) + 
  geom_point(alpha = .5) +
  geom_smooth(method=lm)+
  facet_grid(cols = vars(condition))+ labs(x = "Game length (in Log Minutes)",y = "Points Earned by Group")+theme_classic() + theme(legend.position = "none")
```
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>% 
  ggplot(aes(x = log(gameLength/60), y = groupPoints, color = condition)) + 
  geom_point(alpha = .5) +
  geom_smooth(method=lm)+
  labs(x = "Game length (in Log Minutes)",y = "Points Earned by Group")+theme_classic()
```
### Language x Points
#### Faceted
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>% filter(languageCondition == "Lang") %>%
  ggplot(aes(x = groupNumWords, y = groupPoints, color = condition)) + 
  geom_point(alpha = .5) +
  geom_smooth(method=lm)+
  facet_grid(cols = vars(condition))+ labs(x = "N. Words Exchanged", y = "Group Points (Raw)")+theme_classic() + theme(legend.position = "none")
```
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>% filter(languageCondition == "Lang") %>%
  ggplot(aes(x = groupNumWords, y = adjustedPoints, color = condition)) + 
  geom_point(alpha = .5) +
  geom_smooth(method=lm)+
  facet_grid(cols = vars(condition))+ labs(x = "N. Words Exchanged", y = "Group Points (Adjusted)")+theme_classic() + theme(legend.position = "none")
```
#### Non-Faceted
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>% filter(languageCondition == "Lang") %>%
  ggplot(aes(x = groupNumWords, y = groupPoints, color = condition)) + 
  geom_point(alpha = .5) +
  geom_smooth(method=lm)+
  labs(x = "N. Words Exchanged", y = "Group Points (Raw)")+theme_classic()
```
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>% filter(languageCondition == "Lang") %>%
  ggplot(aes(x = groupNumWords, y = adjustedPoints, color = condition)) + 
  geom_point(alpha = .5) +
  geom_smooth(method=lm)+
  labs(x = "N. Words Exchanged", y = "Group Points (Adjusted)")+theme_classic()
```

@@

@@

```{r, fig.height=3, fig.width=5}
d.round_word_counts %>%left_join(d.games %>% 
                                   select(gameId, condition,chatEnabled)) %>% 
  mutate(languageCondition = ifelse(chatEnabled, "Lang", "Nonlang"),
         fullCondition = paste(condition, languageCondition, sep = "-"),
         block_name = paste0("Block ", blockNum)) %>%
    filter(languageCondition == "Lang") %>%
  group_by(gameId, fullCondition,block_name, trialNum, repNum) %>% 
  summarize(groupNumWords = sum(total_num_words, na.rm = T)) %>%
  ggplot(aes(x = repNum, y = groupNumWords, color = fullCondition)) + 
  geom_point(alpha = .2) +
  geom_smooth(method=lm)+
  facet_grid(cols = vars(block_name)) + labs(x = "Trial Number", y = "N. Words")+ theme_classic()
```

log (n words+1)
```{r, fig.height=3, fig.width=5}
d.round_word_counts %>%left_join(d.games %>% 
                                   select(gameId, condition,chatEnabled)) %>% 
  mutate(languageCondition = ifelse(chatEnabled, "Lang", "Nonlang"),
         fullCondition = paste(condition, languageCondition, sep = "-"),
         block_name = paste0("Block ", blockNum)) %>%
    filter(languageCondition == "Lang") %>%
  group_by(gameId, fullCondition,block_name, trialNum, repNum) %>% 
  summarize(groupNumWords = sum(total_num_words, na.rm = T)+1) %>%
  ggplot(aes(x = repNum, y = log(groupNumWords), color = fullCondition)) + 
  geom_point(alpha = .2) +
  geom_smooth(method=lm)+
  facet_grid(cols = vars(block_name)) + labs(x = "Trial Number", y = "Log (N. Words + 1)")+ theme_classic()
```

@@

```{r, fig.height=3, fig.width=5}
d.round_word_counts %>%left_join(d.games %>% 
                                   select(gameId, condition,chatEnabled)) %>% 
  mutate(languageCondition = ifelse(chatEnabled, "Lang", "Nonlang"),
         fullCondition = paste(condition, languageCondition, sep = "-"),
         block_name = paste0("Block ", blockNum)) %>%
    filter(languageCondition == "Lang") %>%
  group_by(gameId, fullCondition,block_name, trialNum, repNum) %>% 
  summarize(groupNumWords = sum(total_num_words, na.rm = T)) %>%
  filter(groupNumWords > 0) %>%
  ggplot(aes(x = repNum, y = groupNumWords, color = fullCondition)) + 
  geom_point(alpha = .2) +
  geom_smooth(method=lm)+
  facet_grid(cols = vars(block_name)) + labs(x = "Trial Number", y = "N. Words")+ theme_classic()
```

### Accuracy
#### N. Overlap

>>>>

```{r set-up, include=F}
library(tidyverse)
library(jsonlite)
library(here)
source(here("code/preprocessing/00_preprocessing_functions.R"))

#add pretty fonts
library(showtext)
font_add_google(name = "Assistant", family = "Assistant")
font_add_google(name = "Roboto", family = "Roboto")
showtext_auto()

##Data import constants
date_start=lubridate::ymd('2021-07-19')
fig_path=here("figs")
```

```{r}
#colors/theme
bay_palette <- function(num_values) {
  bay_colors <- c(indigo = "#00496F",
                  teal = "#0F85A0",
                        green = "#6B9555",
                        citron = "#ACB64E",
                        yellow = "#edd746",
                        orange = "#E58C35",
                        flame = "#E1672D",
                        red = "#BD3922",
                        maroon = "#903B3D",
                        orchid = "#623D57")
  color_order <- c("teal", "red","green", "flame",  "orchid","indigo", "yellow", "maroon", "citron", "orange")
  num_colors <- length(color_order)
  if (num_values < num_colors) {
    unname(bay_colors[Filter(
      function(color) color %in% color_order[1:num_values],
      names(bay_colors)
    )])
  } else {
    color_indeces <- 0:(num_values - 1) %% num_colors
    unname(bay_colors[color_indeces + 1])
  }
}

scale_colour_bay <- function(...) {
  ggplot2::discrete_scale("colour", "bay", bay_palette, ...)
}

scale_color_bay <- function(...) {
  scale_colour_bay(...)
}

scale_fill_bay <- function(...) {
  ggplot2::discrete_scale("fill", "bay", bay_palette, ...)
}

theme_jmank <- function (base_size = 11, base_family = "Assistant", base_line_size = base_size/22, 
    base_rect_size = base_size/22) 
{
    theme_classic(base_size = base_size, base_family = base_family, 
        base_line_size = base_line_size, base_rect_size = base_rect_size) %+replace% 
        theme(panel.border = element_blank(), panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(), axis.line = element_line(colour = "black", 
                size = rel(1)), legend.key = element_blank(), 
            strip.background = element_rect(fill = "white", colour = "black", 
                size = rel(2)), complete = TRUE) + 
    theme(plot.title = element_text(face = "bold"))
}
```

# Pre-process
Remove joined_data and uncomment the following block to rerun the preprocessing scripts
```{r process-data, message=FALSE, warning=FALSE}
# data_list <- c("technical_pilots", "collabmulti_pilot0",
#                "collabmulti_20", "compet_20", "multi_nonlang_20")
# process_all_data(data_list)
# join_all_data()
```

@@

```{r}
#exclude BLOCKS with <12 completed (all 3 participants responded) rounds
#exclude trial runs
# exclude 
rounds_exclude <- d.rounds %>% group_by(gameId, blockNum) %>% tally() %>% filter(n!=36) %>% select(gameId,blockNum)

d.rounds.final <-  d.rounds %>% left_join(d.games %>% select(gameId, condition)) %>% 
  filter(condition != "coopCartel")%>% anti_join(rounds_exclude)
d.raw_chat.final <- d.raw_chat %>% left_join(d.games %>% select(gameId, condition)) %>% 
  filter(condition != "coopCartel") %>% anti_join(rounds_exclude) %>% write_csv(here("data/processed_data/joined_data/filtered_raw_chat.csv"))
```

@@

d.max_round <- d.contexts %>%
  group_by(gameId, repNum, blockNum, trialNum) %>%
  slice_max(utility, n = 3) %>%
  summarise(roundMax = sum(utility))

d.by_round_metrics <- d.rounds.final  %>% 
  left_join(d.round_word_counts) %>%
  group_by(gameId, trialNum, repNum, blockNum) %>%
  summarize(groupPoints = sum(playerUtility, na.rm = T),
            groupNumWords = sum(total_num_words, na.rm = T),
            groupNumChars = sum(total_num_chars, na.rm = T),
            numFlowers = n_distinct(playerResponse)) %>%
  left_join(d.max_round) %>%
  left_join(game_completion %>% select(gameId, gameComplete)) %>%
  left_join(d.games %>% select(-createdAt)) %>%  
  mutate(languageCondition = ifelse(chatEnabled, "Lang", "Nonlang"),
         fullCondition = paste(condition, languageCondition, sep = "-"),
         roundPointsAdjusted = groupPoints/roundMax)

d.by_block_metrics <- d.by_round_metrics %>% 
  group_by(gameId, name, gameComplete, condition, 
           languageCondition, fullCondition, gameLength, blockNum) %>%
  summarize(blockPoints = sum(groupPoints, na.rm = T),
            blockNumWords = sum(groupNumWords, na.rm = T),
            blockNumChars = sum(groupNumChars, na.rm = T),
            blockMaxPoints = sum(roundMax),
            blockNumFlowers = sum(numFlowers)) %>%
  mutate(blockPointsAdjusted = blockPoints/blockMaxPoints,
         meanNumFlowers = blockNumFlowers*3/(12*3))

d.by_game_metrics <- d.by_block_metrics %>%
  #from this point, only look at completed games
    filter(gameComplete) %>%
  #group by game
  group_by(gameId, name, condition, languageCondition, fullCondition, gameLength) %>%
  summarize(gamePoints = sum(blockPoints, na.rm = T),
            gameNumWords = sum(blockNumWords, na.rm = T),
            gameNumChars = sum(blockNumChars, na.rm = T),
            gameMaxPoints = sum(blockMaxPoints),
            gameNumFlowers = sum(blockNumFlowers)) %>%
  mutate(pointsAdjusted = gamePoints/gameMaxPoints,
         meanNumFlowers = gameNumFlowers*3/ (12*4*3))
```

@@

```{r, fig.height=3, fig.width=5}
d.by_game_metrics%>% 
  ggplot(aes(x = languageCondition, y = gamePoints, color = condition, shape = languageCondition)) + 
  geom_jitter(width = .1, alpha = .5) +
  stat_summary(fun.data = "mean_cl_boot")+
  ylim(0, 1400)+
  facet_grid(cols = vars(condition)) + labs(x = "Language Condition", y = "Points Earned by Group", title = "Points Earned by Group") + scale_color_bay() + theme_jmank() + theme(legend.position = "none")

ggsave(here(fig_path, "points_distirbution_raw.png"), width = 3, height = 5)
```

@@

```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>%
  ggplot(aes(x = languageCondition, y = pointsAdjusted, color = condition, shape = languageCondition)) + 
  geom_jitter(width = .1, alpha = .5) +
  stat_summary(fun.data = "mean_cl_boot")+
  facet_grid(cols = vars(condition)) + 
  labs(x = "Language Condition", 
       y = "Points Earned by Group (Max Adjusted)", 
       title = "Points by Group") + 
  ylim(0,1) +
  scale_color_bay() + theme_jmank() + theme(legend.position = "none")

ggsave(here(fig_path, "points_distirbution_adjusted.png"),  width = 3, height = 5)
```

### Time
```{r, fig.height=5, fig.width=3}
d.by_game_metrics %>%
  ggplot(aes(x = languageCondition, y = gameLength/60, 
             color = condition, shape = languageCondition)) + 
  geom_jitter(width = .1, alpha = .5) +
  stat_summary(fun.data = "mean_cl_boot")+
  facet_grid(cols = vars(condition))+ 
  labs(y = "Time (In Minutes)", title = "Game Length", x = "Language Condition")+
  ylim(0, 90)+
  scale_color_bay() + theme_jmank() +  theme(legend.position = "none")
ggsave(here(fig_path, "time_distirbution.png"),  width = 3, height = 5)

```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>%
  ggplot(aes(x = languageCondition, y = log(gameLength/60), color = condition, shape = languageCondition)) + 
  geom_jitter(width = .1, alpha = .5) +
  stat_summary(fun.data = "mean_cl_boot")+
  facet_grid(cols = vars(condition)) + 
  ylim(0, 4.5)+
  labs(y = "Time (In Log Minutes)", title = "Game Length (Log Mins)")+
  scale_color_bay() + theme_jmank() +  theme(legend.position = "none")

ggsave(here(fig_path, "time_log_distirbution.png"))
```

### Number of Words
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>%
  ggplot(aes(x = languageCondition, y = gameNumWords, color = condition, shape = languageCondition)) + 
  geom_jitter(width = .1, alpha = .5) +
  stat_summary(fun.data = "mean_cl_boot")+
  facet_grid(cols = vars(condition))+ labs(y = "N. Words", title = "Number of Words Exchanged", x = "Language Condition")+scale_color_bay() + theme_jmank() +  theme(legend.position = "none")

ggsave(here(fig_path, "numwords_distirbution.png"), height = 5, width = 3)

```
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>%
  ggplot(aes(x = languageCondition, y = log(gameNumWords+1), color = condition, shape = languageCondition)) + 
  geom_jitter(width = .1, alpha = .5) +
  stat_summary(fun.data = "mean_cl_boot")+
  facet_grid(cols = vars(condition))+ labs(y = "Log N. Words Exchanged")+
  scale_color_bay() + theme_jmank() +  theme(legend.position = "none")
ggsave(here(fig_path, "numwords_log_distirbution.png"))

## Covariate
### Time x Points
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>%
  ggplot(aes(x = gameNumWords, y = gameLength/60, color = condition, shape = languageCondition)) + 
  geom_point(alpha = .5) +
  geom_smooth(method=lm)+ 
  labs(x = "Game length (in Minutes)", y = "Points Earned by Group")+
  scale_color_bay() + theme_jmank() +  theme(legend.position = "none")
ggsave(here(fig_path, "time_words_scatter.png"))
```

```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>%
  ggplot(aes(x = gameLength/60, y = gamePoints, color = log(gameNumWords+1))) + 
  geom_point(alpha = .5) +
  geom_smooth(method=lm, color = "black")+
  facet_grid(cols = vars(condition)) + 
  labs(x = "Game length (in Minutes)", 
       y = "Points Earned by Group",
       color = "Log Num. Words") + 
  theme_jmank() +  scale_color_steps(low = "#0F85A0", high = "#BD3922")

ggsave(here(fig_path, "all_correlated.png"), height = 3, width = 5)
```

```{r, fig.height=3, fig.width=5}
ms <- d.by_game_metrics %>%
  group_by(condition, languageCondition) %>%
  summarise(mean_len = mean(gameLength/60),
            ci_len = 1.96 * sd(gameLength/60) / sqrt(length(gameLength)),
            mean_points = mean(gamePoints),
            ci_points = 1.96 * sd(gamePoints) / sqrt(length(gameLength)))

d.by_game_metrics %>%
  ggplot(aes(x = gameLength/60, y = gamePoints, color = condition, shape = languageCondition)) +#, size = log(groupNumWords+1))) + 
  geom_smooth(aes(group = condition), method = "lm") +
  geom_point(alpha = .2) +
  geom_pointrange(data = ms, aes(x = mean_len, y = mean_points, 
                                 ymin = mean_points - ci_points,
                                 ymax = mean_points + ci_points)) +
  geom_errorbarh(data = ms, aes(x = mean_len, y = mean_points, 
                                 xmin = mean_len - ci_len,
                                 xmax = mean_len + ci_len), width = 0) + 
  # ylim(0,1500) + 
  xlim(0,90) + 
  labs(x = "Game length (in Minutes)", y = "Points Earned by Group")+
  ggthemes::scale_color_solarized() + 
  scale_color_bay() + theme_jmank() +  
  theme(legend.position = "bottom")

ggsave(here(fig_path, "time_points_scatter_nofacet.png"))

```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>% 
  ggplot(aes(x = log(gameLength/60), y = gamePoints, color = condition)) + 
  geom_point(alpha = .5) +
  geom_smooth(method=lm)+
  labs(x = "Game length (in Log Minutes)",y = "Points Earned by Group")+scale_color_bay() + theme_jmank()

ggsave(here(fig_path, "log_time_points_scatter_nofacet.png"))
```
### Language x Points

```{r}
d.by_game_metrics %>% filter(languageCondition == "Lang") %>%
  mutate(langUse = ifelse(gameNumWords > 0, TRUE, FALSE)) %>%
  ggplot(aes(x = gameNumWords, y = gamePoints, color = condition)) + 
  geom_point(alpha = .5) +
  geom_smooth(method=lm)+
  labs(x = "N. Words Exchanged", y = "Group Points (Raw)")+scale_color_bay() + theme_jmank() +  theme(legend.position = "none")

ms <- d.by_game_metrics %>%
  mutate(langUse = ifelse(gameNumWords > 0, TRUE, FALSE)) %>% 
  group_by(condition, fullCondition, languageCondition) %>%
  summarise(mean_nw = mean(gameNumWords),
            ci_nw = 1.96 * sd(gameNumWords) / sqrt(length(gameLength)),
            mean_points = mean(gamePoints),
            ci_points = 1.96 * sd(gamePoints) / sqrt(length(gameLength)))

d.by_game_metrics %>%
  mutate(langUse = ifelse(gameNumWords > 0, TRUE, FALSE)) %>% 
  #filter(langUse) %>%
  ggplot(aes(x = gameNumWords, y = gamePoints, color = condition, shape = languageCondition)) +
  #geom_smooth(aes(group = fullCondition), method = "lm") +
  geom_smooth(aes(group = fullCondition), method=glm, formula=y~poly(x,2), alpha=.3)+
  geom_point( alpha = .5) +
  geom_pointrange(data = ms, aes(x = mean_nw, y = mean_points,
                                ymin = mean_points - ci_points,
                                ymax = mean_points + ci_points)) +
  geom_errorbarh(data = ms, aes(x = mean_nw, y = mean_points,
                                xmin = mean_nw - ci_nw,
                                xmax = mean_nw + ci_nw), width = 0) +
  # ylim(0,1500) + 
  labs(x = "Words Exchanged", y = "Points Earned", title = ) + 
  scale_color_bay() + theme_jmank() +  
  theme(legend.position = "bottom")
```

```{r}
ms <- d.by_game_metrics %>%
  mutate(langUse = ifelse(groupNumWords > 0, TRUE, FALSE)) %>% 
  group_by(condition, langUse) %>%
  summarise(mean_nw = mean(groupNumWords),
            ci_nw = 1.96 * sd(groupNumWords) / sqrt(length(gameLength)),
            mean_points = mean(groupPoints),
            ci_points = 1.96 * sd(groupPoints) / sqrt(length(gameLength)))

d.by_game_metrics %>%
  mutate(langUse = ifelse(groupNumWords > 0, TRUE, FALSE)) %>% 
  ggplot(aes(x = groupNumWords, y = groupPoints, color = condition, shape = langUse)) +
  #geom_smooth(aes(group = condition), method = "lm") +
  geom_point(alpha = .5) +
  geom_pointrange(data = ms, aes(x = mean_nw, y = mean_points, 
                                 ymin = mean_points - ci_points,
                                 ymax = mean_points + ci_points)) +
  geom_errorbarh(data = ms, aes(x = mean_nw, y = mean_points, 
                                 xmin = mean_nw - ci_nw,
                                 xmax = mean_nw + ci_nw), width = 0) + 
  # ylim(0,1500) + 
  labs(x = "Words Echanged", y = "Points Earned") + 
  scale_color_bay() + theme_jmank() +  
  theme(legend.position = "bottom")
```

```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>% filter(languageCondition == "Lang") %>%
  mutate(langUse = ifelse(gameNumWords > 0, TRUE, FALSE)) %>%
  ggplot(aes(x= gameNumWords, y = pointsAdjusted, color = condition, shape = languageCondition)) + 
  geom_point(alpha = .5) +
  geom_smooth(method=lm)+ 
  labs(x = "N. Words Exchanged", y = "Group Points (Adjusted)")+scale_color_bay() + 
  theme_jmank() +  theme(legend.position = "none")

ggsave(here(fig_path, "nwords_points_scatter.png"), height = 3, width = 3)
```

@@

tried to make a gif? :/
```{r}
trial_num = 1
randomGame = sample(game_completion %>% filter(chat == T, gameComplete == T) %>% pull(gameId), 1)

save_plot <- function(rep_Num, block_Num, randomGame) {
  full_data <- d.by_round_metrics %>% 
    filter(repNum == rep_Num, blockNum == block_Num) %>%
  left_join(d.games %>% select(gameId, condition, chatEnabled)) %>% filter(chatEnabled)

  to_plot <- full_data %>% ggplot(aes(x = groupNumWords, y = roundPointsAdjusted, 
                                      shape = condition, color = condition)) + 
    geom_point(alpha = .2) + 
    geom_point(data = full_data %>% filter(gameId == randomGame), aes(x = groupNumWords, y = roundPointsAdjusted, 
                                      shape = condition, color = condition), alpha = 1) + 
    ggtitle(paste0("Block ", blockNum, ", Trial ", repNum))+
  theme_jmank() + scale_color_bay()

  ggsave(to_plot, file = here(fig_path, "animate", paste0(block_Num, "_", rep_Num, ".png")), height = 3, width = 5)
  }
#mapply(save_plot, seq(0,11), rep(0, 12), rep("sTX6ksbxqfnfsmzxe", 12))
```

@@

```{r, fig.height=3, fig.width=5}
d.round_word_counts %>%left_join(d.games %>% 
                                   select(gameId, condition,chatEnabled)) %>% 
  mutate(languageCondition = ifelse(chatEnabled, "Lang", "Nonlang"),
         fullCondition = paste(condition, languageCondition, sep = "-"),
         block_name = paste0("Block ", blockNum)) %>%
    filter(languageCondition == "Lang") %>%
  group_by(gameId, fullCondition,block_name, trialNum, repNum) %>% 
  summarize(groupNumWords = sum(total_num_words, na.rm = T)) %>%
  ggplot(aes(x = repNum, y = groupNumWords, color = fullCondition)) + 
  geom_point(alpha = .2) +
  geom_smooth(method=lm)+
  facet_grid(cols = vars(block_name)) + labs(x = "Trial Number", y = "N. Words")+ scale_color_bay() + theme_jmank()
ggsave(here(fig_path, "nwords_over_time.png"))
```

log (n words+1)
```{r, fig.height=3, fig.width=5}
d.round_word_counts %>%left_join(d.games %>% 
                                   select(gameId, condition,chatEnabled)) %>% 
  mutate(languageCondition = ifelse(chatEnabled, "Lang", "Nonlang"),
         fullCondition = paste(condition, languageCondition, sep = "-"),
         block_name = paste0("Block ", blockNum)) %>%
    filter(languageCondition == "Lang") %>%
  group_by(gameId, fullCondition,block_name, trialNum, repNum) %>% 
  summarize(groupNumWords = sum(total_num_words, na.rm = T)+1) %>%
  ggplot(aes(x = repNum, y = log(groupNumWords), color = fullCondition)) + 
  geom_point(alpha = .2) +
  geom_smooth(method=lm)+
  facet_grid(cols = vars(block_name)) + labs(x = "Trial Number", y = "Log (N. Words + 1)")+ scale_color_bay() + theme_jmank()
ggsave(here(fig_path, "nwords_log_over_time.png"))

@@

```{r, fig.height=3, fig.width=5}
d.round_word_counts %>%left_join(d.games %>% 
                                   select(gameId, condition,chatEnabled)) %>% 
  mutate(languageCondition = ifelse(chatEnabled, "Lang", "Nonlang"),
         fullCondition = paste(condition, languageCondition, sep = "-"),
         block_name = paste0("Block ", blockNum)) %>%
    filter(languageCondition == "Lang") %>%
  group_by(gameId, fullCondition,block_name, trialNum, repNum) %>% 
  summarize(groupNumWords = sum(total_num_words, na.rm = T)) %>%
  filter(groupNumWords > 0) %>%
  ggplot(aes(x = repNum, y = groupNumWords, color = fullCondition)) + 
  geom_point(alpha = .2) +
  geom_smooth(method=lm)+
  facet_grid(cols = vars(block_name)) + labs(x = "Trial Number", y = "N. Words")+ scale_color_bay() + theme_jmank()
```

```{r, fig.height=3, fig.width=5}
d.round_word_counts %>%left_join(d.games %>% 
                                   select(gameId, condition,chatEnabled)) %>% 
  mutate(languageCondition = ifelse(chatEnabled, "Lang", "Nonlang"),
         fullCondition = paste(condition, languageCondition, sep = "-"),
         block_name = paste0("Block ", blockNum)) %>%
    filter(languageCondition == "Lang") %>%
  group_by(gameId, fullCondition,block_name, trialNum, repNum) %>% 
  summarize(groupNumWords = sum(total_num_words, na.rm = T)) %>%
  filter(groupNumWords > 0) %>%
  ggplot(aes(x = repNum, y = log(groupNumWords+1), color = fullCondition)) + 
  geom_point(alpha = .2) +
  geom_smooth(method=lm)+
  facet_grid(cols = vars(block_name)) + labs(x = "Trial Number", y = "N. Words")+ scale_color_bay() + theme_jmank()
```

log num words

```{r, fig.height=3, fig.width=5}
d.round_word_counts %>%left_join(d.games %>% 
                                   select(gameId, condition, chatEnabled)) %>% 
  mutate(languageCondition = ifelse(chatEnabled, "Lang", "Nonlang"),
         fullCondition = paste(condition, languageCondition, sep = "-"),
         block_name = paste0("Block ", blockNum)) %>%
    filter(languageCondition == "Lang") %>%
  group_by(gameId, fullCondition,block_name, trialNum, repNum) %>%

  summarize(groupNumWords = sum(total_num_words, na.rm = T)) %>%
  #filter(groupNumWords >1) %>%
  ggplot(aes(x = repNum, y = log(groupNumWords+1), color = fullCondition)) + 
  geom_point(alpha = .2) +
  geom_smooth(method=lm)+
  ylim(0, 6) +
  facet_grid(cols = vars(block_name)) + labs(x = "Trial Number", y = "N. Words")+ scale_color_bay() + theme_jmank()
```
### Accuracy
#### N. Flowers Selected each round
```{r}
d.rounds.final %>% group_by(gameId, repNum, blockNum, trialNum) %>% 
  summarize(num_unique_flowers = n_distinct(playerResponse),
            mean_response_time = mean(time_sec, na.rm = T))  %>%
  left_join(d.games %>% select(gameId, condition,chatEnabled)) %>% 
  mutate(languageCondition = ifelse(chatEnabled, "Lang", "Nonlang"),
         fullCondition = paste(condition, languageCondition, sep = "-"),
         block_name = paste0("Block ", blockNum)) %>%
    filter(condition != "coopCartel") %>%
  ggplot(aes(x = repNum, y = num_unique_flowers, color = condition, linetype = languageCondition)) + 
  geom_point(alpha = .1) +
  geom_smooth(method=lm)+
  facet_grid(cols = vars(block_name), rows = vars(condition)) + labs(x = "Trial Number", y = "N. Unique Flowers")+ scale_color_bay() + theme_jmank()
```
